---
title: "Assignment4_stat359"
author: "Koki Itagaki"
date: "2023-03-20"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



#Q1. In a study examining smoking and lung cancer, a random sample of men
#between the ages of 55 and 60 was obtained. The smoking and disease status of
#each sampled subject was ascertained. For each subject, a ’1’ is assigned if
#the subject had lung cancer (case) and a ’0’ if not. Similarly, a ’1’ 
#indicates that a subject is a smoker and a ’0’ indicates a nonsmoker.
#The data are found in the Excel file ‘LungCancer’.


#• Read the data into R, and use table() function to produce a contingency
#table summarizing these data.

```{r}
LungCancer<-read.csv(file='~/Desktop/stat359/data/LungCancer.csv',header = TRUE)
observed<-table(LungCancer)
observed

#• Assuming that there is no association between smoking and lung cancer,
#compute a table of ‘expected’ counts.

expected <- round(chisq.test(observed)$expected,2)
expected
#I also did this by hand.
#• By hand, compute the observed value of the test statistic for testing
#association between lung cancer and smoking.
#The result is in a different file

#• Assuming there is no association, what is the distribution of 
#the test statistic?

#If there is no association,the distribution of 
#the test statistic follows a chi-squared distribution with degrees
#of freedom equal to (r-1)(c-1) = (2-1)(2-1) = 1

#• Using R, compute the p-value for a test of association, and give a 
#detailed conclusion based on the p-value and a comparison of the tables 
#observed and expected counts.
1-pchisq(18.63,df = 1)
#Since p-value = 1.587034e-05 << a = 0 .05, we reject Ho. There is a significant 
#evidence that there is an association between Smokers and Cases of lung cancer.
#Also from 2 tables I created above, you can see that the number of cases of the
#lung cancers whose patients are smokers is at least 10 times higher than the
#number of cases of the lung cancers whose patients are non-smokers.
#Therefore the number of cases of the lung cancers is associated with smoking.





```


#2. The following data are from a study examining the incidence of tuberculosis 
#in relation to blood groups in a sample of Eskimos. It is of interest to 
#determine if there is any association between the disease and blood group 
#within the ABO system.
#Severity O A AB B
#Moderate-advanced 7 7 7 13
#Minimal 27 34 12 18
#Not Present 55 52 11 24
#• Assuming that there is no association between disease and blood group, 
#compute a table of ‘expected’ counts.
```{r}
data <- c(7,7,7,13,27,34,12,18,55,52,11,24)

data <- c(7, 7, 7, 13, 27, 34, 12, 18, 55, 52, 11, 24)
mat <- matrix(data, nrow = 3, ncol = 4, byrow = TRUE)

# Calculate the expected counts
row_totals <- rowSums(mat)
col_totals <- colSums(mat)
grand_total <- sum(mat)
e_row <- matrix(row_totals, nrow = nrow(mat), ncol = ncol(mat), byrow = TRUE)
e_col <- matrix(col_totals, nrow = nrow(mat), ncol = ncol(mat), byrow = FALSE)
mat_expected <- e_row * e_col / grand_total

print(mat_expected)
#• By hand, compute the observed value of the test statistic for testing association between
#disease and blood group.

#• Assuming there is no association, what is the distribution of the test statistic?
#If there is no association between the disease and blood group,the distribution of 
#the test statistic follows a chi-squared distribution with degrees
#of freedom equal to (r-1)(c-1) = (3-1)(4-1) = 6
#• Using R, compute the p-value for a test of association, and give a detailed conclusion
#based on the p-value and a comparison of the tables observed and expected counts.

1-pchisq(q = 16.1427,df=6)
#Since p-value = 0.01300819 < a = 0 .05, we reject Ho. There is a significant 
#evidence that there is an association between disease and blood group.
#Also from 2 tables,When I see the row Minimal, The number of cases, which severty
# is Minimal, of people whose blood types arebO and A have almost two time as much as 
#people whose blood type is AB or B.

```
#3. The file ‘Anscombe’ contains 4 diferent datasets, each of which are based on a response Y,
#and a covariate X.
```{r}
ancombe<-read.csv('~/Desktop/stat359/data/anscombe.csv',header=TRUE)



#(a) Produce 4 scatter plots (one for each dataset), on the same page, 
#illustrating the relationship between Y and X. Describe each of these briefly, 
#and state if you think a linear
#model of the form yi = a + bxi + ≤i would be appropriate.
#4
ancombe[45:55,2]
par(mar = c(1,1,1,1))
par(mfrow = c(2,2))
plot(ancombe[2:12,1],ancombe[2:12,2], xlab = "The value of x",
     ylab = "The value of y", main = "Scatterplot of Set1 from anscombe.csv",
     sub = "Written by Koki Itagaki")
plot(ancombe[16:26,1],ancombe[16:26,2], xlab = "The value of x",
     ylab = "The value of y", main = "Scatterplot of Set2 from anscombe.csv",
     sub = "Written by Koki Itagaki")
plot(ancombe[30:40,1],ancombe[30:40,2], xlab = "The value of x",
     ylab = "The value of y", main = "Scatterplot of Set3 from anscombe.csv",
     sub = "Written by Koki Itagaki")
plot(ancombe[45:55,1],ancombe[45:55,2], xlab = "The value of x",
     ylab = "The value of y", main = "Scatterplot of Set4 from anscombe.csv",
     sub = "Written by Koki Itagaki")

#According to the graphs, we can see the different trend of the data.
#Graph 1 shows that there is a positive linear relationships between x and y.
#However, graph 2 is a quadric equation.
#The data from graph 3 also have a  positive relationships between x and y with
#a outlier at arount x = 13 and y = 14.
#There is not a linear relationships in graph 4.The x value of all data is 8 
#except one outlier. it means it does not show any correlation between x and y.
#Therefore, in my opinion,Graph1 and Graph 3 can be shown as yi = a + bxi + error


#(b) Perform 4 separate simple linear regressions (one for each dataset)and 
#produce a table (in your text editor (ie. word)) that shows the R2 value. 
#Discuss what is happening here (hint: for simple linear regression, R2 is just
#the square of the sample correlation coe±cient).

set1_x<-ancombe[2:12,1]
set1_x<-as.numeric(set1_x)
set1_y<-ancombe[2:12,2]
set1_y<-as.numeric(set1_y)
re_set1<-lm(set1_x~set1_y)
re_set1


set2_x<-ancombe[16:26,1]
set2_x<-as.numeric(set2_x)
set2_y<-ancombe[16:26,2]
set2_y<-as.numeric(set2_y)
re_set2<-lm(set2_x~set2_y)
re_set2

set3_x<-ancombe[30:40,1]
set3_x<-as.numeric(set3_x)
set3_y<-ancombe[30:40,2]
set3_y<-as.numeric(set3_y)
re_set3<-lm(set3_x~set3_y)
re_set3

set4_x<-ancombe[45:55,1]
set4_x<-as.numeric(set4_x)
set4_y<-ancombe[45:55,2]
set4_y<-as.numeric(set4_y)
re_set4<-lm(set4_x~set4_y)
re_set4

summary(re_set1)
summary(re_set2)
summary(re_set3)
summary(re_set4)


#Dataset R^2
# 1.   0.67
# 2.   0.67
# 3    0.67
# 4.   0.67

#The Rs of all datasets is the same even though the shapes of 4 graphs are
#totally different. For examle, the first graph shows that there is a linear 
#moderate relationship and the third graph shows that there is a strong linear
#relationships with only one outlier. This means if the data set has at least 
#one outlier, the correlation rate between x and y changes considerably.
#Moreover, the data set 4 shows that quadratic curve and the correlation rate is
#also the same as the dataset 1 and 3.

```
#4. The file ‘growth’ gives data on the height of a white spruce 
#tree measured annually for 50 years. Letting Yt denote the height of the
#tree at year t > 0, we consider describing the growth of the tree over time 
#with a non-linear model Yt = f(t) + ≤t, ≤t iidª N(0;, æ2). Three growth
#curves are considered for f(t)
#(a) Logistic: f(t) = a/(1 + b § exp{°ct})
#(b) Gompertz: f(t) = a exp{°b exp{°ct}}
#(c) Von BertalanÆy: f(t) = a ° a exp{°b(t + c)}
#• Fit all three models using the non-linear least squares function nls() in R.
#Explain how you are choosing the starting values for nls() in each case. 
#Produce a figure depicting the estimated curves all on the same plot, along
#with the observed data. Be sure to include a legend to distinguish the
#diÆerent curves.
```{r}


data <- read.table(file='~/Desktop/stat359/data/growth.txt',header=TRUE)
y <- data$height
t <- data$t
a.start <- max(y)

# Logistic
b.start <- a.start/(min(y))
c.start <- -log((a.start-mean(y))/(b.start*mean(y)))/mean(t)

# Fit logistic model using nls()
logistic <- nls(y ~ a/(1+b*exp(-c*t)), 
                start=list(a=a.start, b=b.start, c=c.start), 
                trace=TRUE)

# Gompertz
b.start <- -log(min(t)/a.start)
c.start <- -log(-log(mean(y)/a.start)/b.start)/mean(t)

# Fit gompertz model using nls()
gompertz <- nls(y ~ a*exp(-b*exp(-c*t)), 
                start=list(a=a.start, b=b.start, c=c.start), 
                trace=TRUE)

# VB
b.start <- -log((mean(y)-a.start)/(min(y)-a.start))/mean(t)
c.start <- -log((a.start-min(y))/a.start)/b.start

# Fit VB model using nls()
vb <- nls(y ~ a*(1-exp(-b*(t+c))), 
          start=list(a=a.start, b=b.start, c=c.start), 
          trace=TRUE)




#I basically find the unknown parameters:a,b,and c for each cases and pass the 
#values to the nls function  to calculate 


# Define a function to generate predictions from a model
predict_model <- function(model, t_values) {
  predicted_values <- predict(model, list(t = t_values))
  return(predicted_values)
}

plot(t, y, xlab = "time in years", ylab = "height in meters")
# predict values for different models
t_seq <- seq(min(t), max(t), 0.01)
H.vb <- predict(vb, list(t = t_seq))
H.gompertz <- predict(gompertz, list(t = t_seq))
H.logistic <- predict(logistic, list(t = t_seq))

# add lines to the plot for each model
lines(t_seq, H.vb, col = "yellow")
lines(t_seq, H.gompertz, col = "blue")
lines(t_seq, H.logistic, col = "green")

# add a legend to the plot
legend(x = 5, y = 40, legend = c("VB", "Gompertz", "Logistic"), fill = c("yellow", "blue", "green"))

#• For each of the three models, give a 95% confidence interval for limt!1f(t).
#What doest his represent?
z<-1.96
paste("95% CI for the first model is: ",74.411938 -z*9.950934 , 74.411938 +z*9.950934,
  "95% CI for the second model is: ",50.4208-z*0.8473 , 50.4208 +z*0.8473,
  "95% CI for the third model is: ",52.21789 -z*1.33361 , 52.21789 +z*1.33361 )
t.plot <- seq(min(t), max(t), 0.01)



#• Select the best of the three models, and plot an estimate of the
#derivative df(t) dt , which represents the rate of growth over time.

# define variables a, b, and c
a <- 50.4208; b <- 47.1377; c <- 0.1993

# calculate the derivative of Y with respect to time
deriva <- a*b*c*exp(-c * t.plot) / ((1 + b * exp(-c * t.plot))^2)

plot(deriva,main = "estimate of the derivative")


```
