---
title: "Assignment5_stat359"
author: "Koki Itagaki"
date: "2023-03-27"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#1. Beef consumption (in pounds per capita) in the United States between 1922 
and 1941 are given in the data set beef.txt. Other variables of interest are
beef price (in cents per pound divided by CPI), income (disposable income 
capita in dollars divided by the CPI), and pork consumption(pounds per capita).
[CPI= Consumer price index]. Find a model that best describes beef consumption
in the United States. Complete a full analysis of the data (initial plots,
model selection, residual plots etc.). Discuss your results.
```{r}
beef<-read.table(file='~/Desktop/stat359/data/beef.txt', header = T)
attach(beef)
head(beef)
dim(beef)
par(mar = c(4,4,2,2))
pairs(beef)


#From the graph, it is not clear the relationships between 
#beef consumption and price. There is a positive trend between beef consumption
#and income.For the plot of beef consumption and pork consumption, it seemsto be
#that there is quadratic relationship. First of all,I will do backward selection

model1<-lm(Beef.Consumption~Price*Income*Pork.Consumption+I(Pork.Consumption^2))
summary(model1)
#I(Pork.Consumption^2) is the least significant(p-value = 0.1208)

model2<-update(model1,.~.- I(Pork.Consumption^2))
summary(model2)

#Price x Income x Pork.Consumption is not significant(p-value = 0.0970)
#so I remove it.

model3<-update(model2,.~.- Price:Income:Pork.Consumption)
summary(model3)
#Income x Pork.Consumption is not significant(p-value = 0.4034) and is removed

model4<-update(model3,.~.- Income:Pork.Consumption)
summary(model4)
#Price x Income is not significant(p-value = 0.501) and is removed

model5<-update(model4, .~. -Price:Income)
summary(model5)
#Price x Pork.Consumption is not significant(p-value = 0.0657) and is removed


model6<-update(model5,.~. -Price:Pork.Consumption)
summary(model6)
par(mfrow = c(1,3))
plot(model6,which = c(1,2,4))
#Now, R^2 is 0.9212 which is considerably high and the coefficient estimates 
#appear stable and all the effects are significant.Now I check the three 
#important plots.
#It is clear that the variance of residuals is now constant 
#from Residuals vs Fitted plot. Moreover, the qq plot describes that the 
#distribution of the residuals is normally distributed. However, the graph
#of Cooks distance shows that the observation 20 is the most influential element
#so i remove it and see the result 

model7<-update(model6,.~.,subset=(1:length(Beef.Consumption)!=20))
summary(model7)
par(mfrow = c(1,3))
plot(model7,which = c(1,2,4))
confint(model7)
```
In conclusion,price, income,and pork consumption as main effects are related to the mean of 
beef comsumption ,but the interaction of any variables are not related.
The equation is 
Beef.Consumption = 89.400665 +Price*-1.894812 + Income*0.089333 + Pork.Consumption*-0.420366
Also It is clear that there is a postive relationship between beef consumption
and Income. When one unit increases in income, the beef consumption increases by
0.089333. On the other hand, there are negative relationships between 
beef consumption and price,and between beef consumption and pork consumption.
When one unit increases in price, the beef consumption decreases by
1.894812 When one unit increases in pork consumption, the beef consumption
decreases by 0.420366.
The 95% Confidence nterval of intercept is (78.00857212, 100.7927589).
The 95% Confidence interval of Price is (-2.21318371, -1.5764406).
The 95% Confidence interval of Income is (0.07103601,   0.1076305).
The 95% Confidence interval of Pork.Consumption is (-0.53445295  -0.3062786).
The variance of residuals is constant and the qq plot shows that the graph 
is normally distributed. However, R^2 is 0.9191 which means the graph explains
the variability of the distribution by Price,Income and Pork.Consumption.
Therefore, this model is adequate since The variance of residuals is constant,
and it is normally distributed. Also R^2 is pretty high.





#2. It is well known that the concentrations of cholesterol in
blood serum increases with age, but it is less clear whether
cholesterol level is also associated with body weight. The
data set chol.txt contains data for 30 women and has
measures of serum cholesterol (CHOL) in millimoles per
liter, age (years) and body mass index (BMI). Use multiple
regression to test whether serum cholesterol is associated
with body mass index when age is included in the model.
Consider carefully how both variables should be included,
include initial plots, residual plots etc. Discuss your results
carefully.


```{r}
chol <- read.table(file ='~/Desktop/stat359/data/chol.txt',header=TRUE,sep="")
attach(chol)
head(chol)
summary(chol)
pairs(chol)

#From the graphs, it is clear that there is a positive linear relationship 
#between serum cholesterol (CHOL) and body mass index. Also there is a positive
#linear relationship between serum cholesterol (CHOL) and Age. So I start with
#the model which will has 2 main effects:Age and BMI and the interaction of Age
#and BMI.



model <- lm(CHOL ~ Age * BMI, data = chol)
summary(model)

#This initial model has an R^2 = 0.4743 which is considerably small, and 
#the interaction term is not significant.So, I will remove it from the model and
#keep fitting the model with the rest of the data.


model2<-update(model, .~. - Age:BMI)
summary(model2)

#This second model has an R^2 = 0.4654 which is stil very small but now all of
#effects are significant. Then I will check the 3 important graphs now.
par(mfrow = c(1,3))
plot(model2, which = c(1,2,4))
#It is clear that the variance of residuals is not constant and increases with
#fitted values from Residuals vs Fitted plot.
#Moreover, the qq plot shows that the graph might be right skewed
#Now, I use log tranformation to make the model better.




model3<-lm(log(CHOL)~Age+BMI, data = chol)

summary(model3)
par(mfrow = c(1,3))
plot(model3, which = c(1,2,4))


#Now the variance of the residuals looks constant, and the distribution of the 
#residuals also normally distributed.However,observation 24 might be potentially
#influential. So I will remove the observation.

model4<-update(model3,.~.,subset =(1:length(CHOL)!= 24))
summary(model4)
par(mfrow = c(1,3))
plot(model4, which = c(1,2,4))

#After removing observation 24, the coefficient estimates appear stable
#and also R^2 is stable. However, when I see the plots, model3 has more constant 
#variance of the residuals, and it is more normally distributed.
#So, I will use model3 in this case as the result.



summary(model3)
par(mfrow = c(1,3))
plot(model3, which = c(1,2,4))
confint(model3)

```
In conclusion,age and BMI is related to the mean of log concentrations of cholesterol in
blood serum,but the interaction of age and BMI is not related.
The equation is log(CHOL) = 0.5483 + Age*0.006449 + BMI*0.038581
Also It is clear that BMI is more assortiated with the mean of cholesterol level
than Age.Everytime when one unit increases in BMI, log Chol increases by 0.038581 which 
is much higher than increasing one unit of age which lead log CHOL to increase
by 0.001779404.
The 95% Confidence interval of intercept is (-0.101383385, 1.19790770).
The 95% Confidence interval of Age is (0.001779404, 0.01111773 ).
The 95% Confidence interval of BMI is (0.008176087 0.06898639 ).

The variance of residuals is constant and the qq plot shows that the graph 
is normally distributed.However, R^2 is 0.4787 which means only half
of variability can be explained by Age and BMI.
However,this model is adequate since The variance of residuals is constant,and
it is normally distributed.





